### 2019-02-12 manuscript/results.tex
More results, fixing figure 2

\subsection{Diploidization as an exploratory hypothesis}
In the D/P model  the diploidization rate $\delta$ and polyploidization rate $\rho$ are different from zero with probability 1. Diploidization rate is more uncertain than polyploidization. For the D/p no $\delta$ model, the polyploidization rate is still different from zero but has a wider 95\% credible interval (see Supplementary Information).

For the models containing both polyploidy and breeding system traits, we found that the diploidization rate is really uncertain with a MAP that is (CALCULATE VALUE HERE- close to zero). The polyploidization rate from self-incompatible diploid $\rho_I$ is slightly faster than the polyploidization rate from self-compatible diploid $\rho_C$

>>>>

\subsection{Diploidization as an exploratory hypothesis}
In the D/P model  the diploidization rate $\delta$ and polyploidization rate $\rho$ are different from zero with probability 1. Diploidization rate is more uncertain than polyploidization. For the D/P no $\delta$ model, the polyploidization rate is still different from zero but has a wider 95\% credible interval (see Supplementary Information). In the D/P-A/B model the diploidization rate remains positive but there rate of polyploidization becomes really uncertain. Whereas, in the absence of diploidzation (D/P no $\delta$ A/B) the rate of polyploidy has a small credible interval \newline

For the model ID/P/CD containing both polyploidy and breeding system traits, we found that the diploidization rate is really uncertain with a MAP that is (CALCULATE VALUE HERE- close to zero). The polyploidization rate from self-incompatible diploid $\rho_I$ is slightly faster than the polyploidization rate from self-compatible diploid $\rho_C$  and that pattern remains the same for the ID/P no $\delta$/CD model(see supplementary information).
%Here I'm missing the MuHiSSE plots.

\subsection{Model selection}

In \cref{table:marginallike} we list the marginal likelihood in log scale for each of the models tested. In the table we show what are the different components included and excluded for each model as a a summary of the diagrams from \cref{figure:netdivall}. From the marginal likelihoods in log scale, the Bayes factors in log-scale were calculated as shown in table \cref{table:bayesfactors}. After testing every single pair of polyploidy modes (1-4) we found overwhelming evidence that the best polyploidy model is always  the D/P-A/B, that is the model with hidden state and diploidization. \newline
For the two models following the evolution of breeding system, the I/C-A/B is the best choice between models 3 and 4.\newline
The models that follow the diversification linked to both polyploidy and breeding system are the last 4 (models 5-8). When comparing using Bayes factores every two models we found that the IC/P/CD-A/B is always preferred over the rest, meaning that the model that has a hidden state and diploidization is chosen over the ones that lack either of both of those options.\newline
Therefore, the models that were chosen were always the ones containing a hidden trait, and in the case of polyploidy models, the ones containing a diploidization parameter $\delta$ are preferable.
